### 2017-01-20 paper2.tex
Made Christine's revisions

\setcounter{pageFix}{\value{page}}
\begin{abstract}
\thispagestyle{fancy}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}
    We present the first cosmological galaxy evolved using the modern smoothed
    particle hydrodynamics (SPH) code \textsc{GASOLINE2} with superbubble
    feedback.  We show that superbubble-driven galactic outflows powered by Type
    II supernovae alone can produce $\rm{L^*}$ galaxies with flat rotation
    curves with circular velocities $\sim 200\; \rm{km/s}$, low bulge-to-disc
    ratios, and stellar mass fractions that match observed values from high
    redshift to the present.  These features are made possible by the high mass
    loadings generated by the evaporative growth of superbubbles.  Outflows are
    driven extremely effectively at high redshift, expelling gas at early times
    and preventing overproduction of stars before $z=2$.  Centrally
    concentrated gas in previous simulations has often lead to unrealistically
    high bulge to total ratios and strongly peaked rotation curves.  We show that
    supernova-powered superbubbles alone can produce galaxies that agree well
    with observed properties without the need for additional feedback mechanisms
    or increased feedback energy.   We present additional results arising from
    properly modelled hot feedback.
\end{abstract}

@@

In addition to increasing the total amount of energy deposited by stellar
feedback, these models often also include components designed to prevent energy
from feedback radiating away (a problem discussed thoroughly in
\citealt{Thacker2000}).   The energy can be prevented from cooling completely
for a while \citep{Stinson2013} or it can be initially placed into a non-cooling
reservoir that leaks back into regular thermal energy \citep{Agertz2013}.
Alternately, depositing thermal feedback into a sufficiently small mass, allows
it to always heat gas to the same high temperature where cooling times are long
\citep{DallaVecchia2012}.  Depositing feedback as kinetic avoids initial
radiative losses \citet{Springel2003,Agertz2013,Hopkins2013}.

@@

We compare four test cases using the same initial conditions: no stellar
feedback (an absolute lower bound for looking at the effects of feedback);
superbubble feedback (our fiducial case); blastwave feedback (the feedback
method used in \citet{Stinson2010}, first described in \citealt{Stinson2006}); and
superbubble feedback with double the standard feedback energy ($2\times10^{51}\;
\rm{erg}$ per SN).  The high feedback energy case uses more feedback than is
predicted by \citet{Leitherer1999}, but is within the range of feedback energies
currently being used in cosmological simulations \citep{Schaye2015, Agertz2015,
Vogelsberger2013}.

Halos were found in each of the simulations using the Amiga Halo Finder
\citep[AHF;][]{Knollmann2009}.

@@

The feedback recipe used in our main simulations is the superbubble method
presented in \citet{Keller2014}.  This method deposits feedback into resolution
elements in a brief multi-phase state.  These particles each have separate
specific energies, masses and densities, for the hot bubble and surrounding cold
ISM, which includes the swept up shell.  This allows the method to calculate a
separate density and cooling time with the respective densities for each phase,
rather than the average density of both phases.  Multiphase particles are also
prevented from forming stars: the average temperature of the two phases is
essentially always above our temperature threshold for star formation.  More
details on this method can be found in \citet{Keller2014}.

@@

\subsection{Halo Evolution and Star Formation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures2/net_accretion.eps}
    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}
    \label{net_accretion2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/inflowoutflow.eps}
    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }
    \label{inflow_outflow2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_netflux.eps}
    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}
        \label{angular_momentum_netflux2}
\end{figure}
Ejecting baryons from the disc is essential to producing galaxies that fit the
$M_*/M_{halo}$ relationship predicted by \citet{Behroozi2013},
\citet{Moster2013} and others.  As Figures~\ref{mass_growth2}
and~\ref{stellar_fraction2} show, the galaxies either lacking feedback or using
blastwave feedback alone fail to regulate star formation, diverging from the
expected abundance matching relation at $z\sim3$ for the blastwave, and before
$z=5$ without feedback, giving galaxies that lie above the abundance-matching
relationships over nearly their entire history and mass evolution.  With
superbubble feedback, this galaxy lies within the range of observed stellar
masses over its entire evolution, although on the low side of this range at low
redshift.  Arbitrarily increasing feedback energies, despite having reasonable
star formation rates near $z=0$, under produces stars for most cosmic history,
giving stellar masses {\it lower} than predicted by abundance matching.  Stellar
and total masses were calculated for the region inside $R_{vir}$.  As the halo
grows over time, brief reductions in the stellar mass fraction can be seen for
the no-feedback and blastwave feedback halos in Figure~\ref{stellar_fraction2},
simply by the accretion of gas and dark matter that has not yet made it to the
galaxy disc.  Once these mergers complete, the stellar fraction rate leaps up
once again because of the new supply of gas.  The relative flatness in this
figure at low redshift is reflected in the relative flatness in the star
formation rate, shown in figure~\ref{sfr2}.  This is simply a side effect of the
massive star formation rates at high redshift:  the bulk of star forming gas has
been consumed, and thus star formation has slowed.

@@

As figure~\ref{massloading2} shows, the outflow behavior of this galaxy is
fundamentally different when superbubble feedback is used.  The wind mass
loading factor $\eta = \dot M_{outflow} / \dot M_*$, a measure of how
efficiently feedback is generating outflows, is roughly an order of magnitude
larger during the bursts of star formation from $z=4-2$, expelling a large
amount of gas from the disc early on.  The resulting suppression of
high-redshift star formation is key to obtaining the correct stellar mass
relation as the halo grows, is unmistakable in figure~\ref{mass_growth2}
and~\ref{stellar_fraction2}.  Evidence of these outflows can be seen in the $z=0$
column density images in figure~\ref{column_density2}.  High-latitude neutral
hydrogen from both ejected and infalling material can be seen in the two
superbubble cases, but is totally absent otherwise.  The smaller amount seen
around the high feedback energy case is simply due to this gas being expelled
further.  The reason superbubbles are so effective at removing mass from the
galaxy and thus regulating the stellar mass depends both on the higher outflow
rates as well as the lower star formation rates needed to drive these outflows,
leading to much larger mass loading factors than the blastwave model can
achieve.  This is clearly shown in figure~\ref{massloading2}, as the top panel is
essentially the middle panel divided by the bottom panel.  The outflow rates
driven by superbubbles is at most $\sim2$ times greater than the blastwave model,
but since this is driven by a comparatively tiny amount of star formation, the
massloading, $\eta$, is nearly 10 times greater at high redshift.  The factor of
$\sim2$ higher outflow rate is what we would expect from the roughly $\sim2$
larger baryon depletion from the superbubble vs. blastwave cases.

The effectiveness of the superbubble-driven galactic winds can be clearly seen
in figure~\ref{net_accretion2}, where the net accretion of stars and gas is
greatly reduced by the use of superbubble feedback, resulting at $z=1$ in a net
reduction in the total baryonic mass inside $0.5R_{vir}$ of $\sim14\%$ vs.
blastwave feedback, and $\sim30\%$ vs. no feedback whatsoever (along with the 
removal of baryons from the disc discussed earlier. As the outflow
rate drops towards $z=0$, much of this ejected material falls back onto the
disc, and the outflows transition to a fountain mode, actually increasing
the inflow rate seen compared to the blastwave feedback case in
figure~\ref{inflow_outflow2}.  This increase in the accretion of gas fuels an
equivalent increase in star formation, as is seen in figures~\ref{sfr2}
and~\ref{massloading2}.

@@

Our resolution limits the formation of dense structures in the ISM.  The lack of
resolved dense gas means that feedback processes involved in disrupting
molecular clouds (UV photodissociation, radiation pressure, etc.) is largely
irrelevant for these simulations.  In fact, since much of the energy from early
stellar feedback is consumed in the disruption of the densest clouds in
simulations such as this, the addition of this energy may be unrealistic,
effectively double counting energy that would have been used to disrupt clouds.
Furthermore, high-resolution studies of individual molecular clouds have found
that ionizing radiation, despite disrupting these clouds, ultimately only
imparts $\lesssim 0.1\%$ of the total radiative luminosity to the gas in the
cloud and the surrounding medium in the form of additional thermal and kinetic
energy \citep{Dale2005, Gendelev2012, Walch2012}).  Thus, applying even as
little as $1\%$ of the radiative luminosity as a source of feedback in a
simulation that does not resolve structure within molecular clouds is likely
massively overestimating the impact on disc scales.

>>>>

\setcounter{pageFix}{\value{page}}
\begin{abstract}
\thispagestyle{fancy}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}
    We present the first cosmological galaxy evolved using the modern smoothed
    particle hydrodynamics (SPH) code \textsc{GASOLINE2} with superbubble
    feedback.  We show that superbubble-driven galactic outflows powered by Type
    II supernovae alone can produce $\rm{L^*}$ galaxies with flat rotation
    curves with circular velocities $\sim 200\; \rm{km/s}$, low bulge-to-disc
    ratios, and stellar mass fractions that match observed values from high
    redshift to the present.  These features are made possible by the high mass
    loadings generated by the evaporative growth of superbubbles.  Outflows are
    driven extremely effectively at high redshift, expelling gas at early times
    and preventing overproduction of stars before $z=2$.  Centrally
    concentrated gas in previous simulations has often led to unrealistically
    high bulge to total ratios and strongly peaked rotation curves.  We show that
    supernova-powered superbubbles alone can produce galaxies that agree well
    with observed properties without the need for additional feedback mechanisms
    or increased feedback energy.   We present additional results arising from
    properly modelled hot feedback.
\end{abstract}

@@

In addition to increasing the total amount of energy deposited by stellar
feedback, these models often also include components designed to prevent energy
from feedback radiating away (a problem discussed thoroughly in
\citealt{Thacker2000}).   The energy can be prevented from cooling completely
for a while \citep{Stinson2013} or it can be initially placed into a non-cooling
reservoir that leaks back into regular thermal energy \citep{Agertz2013}.
Alternately, depositing thermal feedback into a sufficiently small mass, allows
it to always heat gas to the same high temperature where cooling times are long
\citep{DallaVecchia2012}.  Depositing feedback as kinetic energy avoids initial
radiative losses \citet{Springel2003,Agertz2013,Hopkins2013}.

@@

We compare four test cases using the same initial conditions: no stellar
feedback (an absolute lower bound for looking at the effects of feedback);
superbubble feedback (our fiducial case); blastwave feedback (a cooling-shutoff
based method, and the feedback method used in \citet{Stinson2010}, first
described in \citealt{Stinson2006}); and superbubble feedback with double the
standard feedback energy ($2\times10^{51}\; \rm{erg}$ per SN).  The high
feedback energy case uses more feedback than is predicted by
\citet{Leitherer1999}, but is within the range of feedback energies currently
being used in cosmological simulations \citep{Schaye2015, Agertz2015,
Vogelsberger2013}.

Halos were found in each of the cosmological simulations using the Amiga Halo
Finder \citep[AHF;][]{Knollmann2009}.

@@

The feedback recipe used in our main simulations is the superbubble method
presented in \citet{Keller2014}.  This method deposits feedback into resolution
elements in a brief multi-phase state.  These particles each have separate
specific energies, masses and densities, for the hot bubble and surrounding cold
ISM, which includes the swept up shell.  This allows the method to calculate a
separate density and cooling time with the respective densities for each phase,
rather than the average density of both phases.  Multiphase particles are also
prevented from forming stars: the average temperature of the two phases is
essentially always above our temperature threshold for star formation, and they
also rapidly become too diffuse to form stars as well.  More
details on this method can be found in \citet{Keller2014}.

@@

\subsection{Halo Evolution and Star Formation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures2/net_accretion.eps}
    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (inflow minus outflow of stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}
    \label{net_accretion2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/inflowoutflow.eps}
    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }
    \label{inflow_outflow2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_netflux.eps}
    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}
        \label{angular_momentum_netflux2}
\end{figure}
Ejecting baryons from the disc is essential to producing galaxies that fit the
$M_*/M_{halo}$ relationship predicted by \citet{Behroozi2013},
\citet{Moster2013} and others.  As Figures~\ref{mass_growth2}
and~\ref{stellar_fraction2} show, the galaxies either lacking feedback or using
blastwave feedback alone fail to regulate star formation, diverging from the
expected abundance matching stellar mass to halo mass relation at $z\sim3$ for
the blastwave, and before $z=5$ without feedback, giving galaxies that lie above
the abundance-matching relationships over nearly their entire history and mass
evolution.  With superbubble feedback, this galaxy lies within the range of
observed stellar masses over its entire evolution, although on the low side of
this range at low redshift.  Arbitrarily increasing feedback energies, despite
having reasonable star formation rates near $z=0$, under produces stars for most
cosmic history, giving stellar masses {\it lower} than predicted by abundance
matching.  Stellar and total masses were calculated for the region inside
$R_{vir}$.  As the halo grows over time, brief reductions in the stellar mass
fraction can be seen for the no-feedback and blastwave feedback halos in
Figure~\ref{stellar_fraction2}, simply by the accretion of gas and dark matter
that has not yet made it to the galaxy disc.  Once these mergers complete, the
stellar fraction rate leaps up once again because of the new supply of gas.  The
relative flatness in this figure at low redshift is reflected in the relative
flatness in the star formation rate, shown in figure~\ref{sfr2}.  This is simply
a side effect of the massive star formation rates at high redshift:  the bulk of
star forming gas has been consumed, and thus star formation has slowed.

@@

As figure~\ref{massloading2} shows, the outflow behavior of this galaxy is
fundamentally different when superbubble feedback is used.  The wind mass
loading factor $\eta = \dot M_{outflow} / \dot M_*$, a measure of how
efficiently feedback is generating outflows, is roughly an order of magnitude
larger during the bursts of star formation from $z=4-2$, expelling a large
amount of gas from the disc early on.  The resulting suppression of
high-redshift star formation is key to obtaining the correct stellar mass
relation as the halo grows, which is unmistakable in figure~\ref{mass_growth2}
and~\ref{stellar_fraction2}.  Evidence of these outflows can be seen in the $z=0$
column density images in figure~\ref{column_density2}.  High-latitude neutral
hydrogen from both ejected and infalling material can be seen in the two
superbubble cases, but is totally absent otherwise.  The smaller amount seen
around the high feedback energy case is simply due to this gas being expelled
further.  The reason superbubbles are so effective at removing mass from the
galaxy and thus regulating the stellar mass depends both on the higher outflow
rates as well as the lower star formation rates needed to drive these outflows,
leading to much larger mass loading factors than the blastwave model can
achieve.  This is clearly shown in figure~\ref{massloading2}, as the top panel is
essentially the middle panel divided by the bottom panel.  The outflow rates
driven by superbubbles is at most $\sim2$ times greater than the blastwave model,
but since this is driven by a comparatively tiny amount of star formation, the
massloading, $\eta$, is nearly 10 times greater at high redshift.  The factor of
$\sim2$ higher outflow rate is what we would expect from the roughly $\sim2$
larger baryon depletion from the superbubble vs. blastwave cases.

The effectiveness of the superbubble-driven galactic winds can be clearly seen
in figure~\ref{net_accretion2}, where the net accretion of stars and gas is
greatly reduced by the use of superbubble feedback, resulting at $z=1$ in a net
reduction in the total baryonic mass inside $0.5R_{vir}$ of $\sim14\%$ vs.
blastwave feedback, and $\sim30\%$ vs. no feedback whatsoever (along with the 
removal of baryons from the disc discussed earlier). As the outflow
rate drops towards $z=0$, much of this ejected material falls back onto the
disc, and the outflows transition to a fountain mode, actually increasing
the inflow rate seen compared to the blastwave feedback case in
figure~\ref{inflow_outflow2}.  This increase in the accretion of gas fuels an
equivalent increase in star formation, as is seen in figures~\ref{sfr2}
and~\ref{massloading2}.

@@

Our resolution limits the formation of dense structures in the ISM.  The lack of
resolved dense gas means that feedback processes involved in disrupting
molecular clouds (UV photodissociation, radiation pressure, etc.) are largely
irrelevant for these simulations.  In fact, since much of the energy from early
stellar feedback is consumed in the disruption of the densest clouds in
simulations such as this, the addition of this energy may be unrealistic,
effectively double counting energy that would have been used to disrupt clouds.
Furthermore, high-resolution studies of individual molecular clouds have found
that ionizing radiation, despite disrupting these clouds, ultimately only
imparts $\lesssim 0.1\%$ of the total radiative luminosity to the gas in the
cloud and the surrounding medium in the form of additional thermal and kinetic
energy \citep{Dale2005, Gendelev2012, Walch2012}).  Thus, applying even as
little as $1\%$ of the radiative luminosity as a source of feedback in a
simulation that does not resolve structure within molecular clouds is likely
massively overestimating the impact on disc scales.
